Object-Oriented Internet\\ Cloud Interoperability

### 2021-01-10 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
Make the manuscripts of up to 14 pages long #58
- reviewed full text
- now it contains 14 pages
- improved graphics against text modification
Make the manuscripts of up to 14 pages long #58
- replaced Azure by cloud where possible
- added environment proposition} to stress our outcome
- fixes #58

%Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect. \ref{cloud-to-sensors-field-level-connectivity}). By design, the \textbf{direct} approach requires that the cloud has to be compliant with the interoperability standard the CPS is built upon - it becomes a consistent part of the CPS. Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in a general case. A more detailed description is covered by the Sect.~\ref{cloud-to-sensors-field-level-connectivity}.

@@

\begin{itemize}
      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
\end{itemize}

@@

% The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security - context differences to name only a few. The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogeneous environments in concern. The proposed implementation is designed for a selected interoperability standard and cloud product.

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification. According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting Azure/PubSub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result, the prototyping is to be limited to implementation of the \emph{Embedded\ Gateway} software part only.

@@

\begin{wrapfigure}{r}{0.55\textwidth}
      \includegraphics[width=0.53\textwidth]{UADataApplicationArchitecture.eps}
      \caption{Reactive interoperability architecture}\label{figure2.UADataApplicationArchitecture}
\end{wrapfigure}

@@

\section{Azure - OOI Interoperability Implementation}\label{section.gateway-implementation}

@@

A generic domain model presenting interconnection architecture between the Azure \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}. It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig. \ref{figure2.UADataApplicationArchitecture}). Merging selected entities of this archetype into the proposed domain model (Fig. \ref{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig. \ref{figure3.ImplementationDomainModel}. In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.

@@

In the final deployment architecture (Fig. \ref{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library. \emph{Networking} (SDK) was removed from this diagram for the sake of simplicity. Instantiating \emph{PartDataManagementSetup} is the first step for bootstrapping process of the \emph{Consumer} role functionality. This class provides an entry point to initialize all properties, which are injection points of all parts composing this role. It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes:

\begin{itemize}
      \item \emph{PartBindingFactory} - to gather the data recovered from the \emph{Message} instances pulled from the wire
      \item \emph{CommunicationContext} - to handle communication with the Azure services
\end{itemize}

The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the Azure services using the configured out-of-band protocol.

%\emph{IEncodingFactory} and \emph{IMessageHandlerFactory} interfaces (Fig. \ref{figure2.UADataApplicationArchitecture}) have been implemented in independent libraries and ae not considered for any modifications to deploy \emph{Embedded Gateway} functionality. The current implementation of the mentioned interfaces is localized at run time as services using an instance of the \emph{IServiceLocator}\footnote{ \url{https://www.nuget.org/packages/CommonServiceLocator} }. In this example, it is assumed that \emph{IServiceLocator} is implemented to resolve references to any external services. Both interfaces are used to manage the interconnection of the node with the \emph{Cyber-physical Network}.

\begin{wrapfigure}{t}{0.55\textwidth}
      \includegraphics[width=0.53\textwidth]{ImplementationArchitecture.eps}
      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
\end{wrapfigure}

The Azure interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.

@@

The encoded JSON messages must be transferred to Azure over the network using the selected protocol stack. The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones. Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity. In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility. Alternatively, the API offered by the dedicated frameworks (libraries) may be used. Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features. In the proposed implementation, the Azure interconnection has been obtained using the mentioned above frameworks.

@@

We derived the final model presented in Fig. \ref{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig. \ref{figure1.StrategyDomainModel}). In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as as a composable part aggregated by the \emph{Reactive Application}.

>>>>

@@

\begin{itemize}
      \item reactive M2M interoperability based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
      \item cloud interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
\end{itemize}

@@

@@

Based on the sessionless and session-oriented communication patterns examination against the IoT requirements \cite{mpostol2020} it could be concluded that the connectionless pattern better suites issues related to the assets mobility and traffic asymmetry that is characteristic for the application domains in concern. Additionally, to promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub  specification. According to proposed generic architecture (Fig.~\ref{figure1.StrategyDomainModel}) to implement the \emph{Embedded\ Gateway} as a composable part of the \emph{Cyber-physical\ node} a library implementing \emph{Networking} functionality in compliance with mentioned above specification is a starting point for further development. Additionally, it must be assumed that the library used to deploy \emph{Embedded\ Gateway} supports dependency injection and is capable to compose an external part supporting cloud/PubSub gateway functionality. The composition process must be available without modification of the core code of an existing library. As a result, the prototyping is to be limited to implementation of the \emph{Embedded\ Gateway} software part only.

@@

\begin{wrapfigure}{r}{0.55\textwidth}
      \includegraphics[width=0.53\textwidth]{UADataApplicationArchitectureAzure.eps}
      \caption{Reactive interoperability architecture}\label{figure2.UADataApplicationArchitecture}
\end{wrapfigure}

@@

\section{Cloud - OOI Interoperability Implementation}\label{section.gateway-implementation}

\begin{proposition}
      A generic domain model presenting interconnection architecture between the \emph{Cloud-based\ Front-end} and \emph{Cyber-physical\ node} attached to the \emph{Cyber-physical\ network} is presented in Fig.~\ref{figure1.StrategyDomainModel}. It is proposed to implement the \emph{Cyber-physical\ node} by adopting the \emph{Reactive Application} archetype compliant with the reactive interoperability concept (Fig. \ref{figure2.UADataApplicationArchitecture}). Merging selected entities of this archetype into the proposed domain model (Fig. \ref{figure1.StrategyDomainModel}) lead to a model expressed as the diagram presented in Fig. \ref{figure3.ImplementationDomainModel}. In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.
\end{proposition}

@@

@@

In the final deployment architecture (Fig. \ref{figure4.ImplementationArchitecture}) the \emph{Consumer} role has been realized by the \emph{PartDataManagementSetup} that is derived from \emph{DataManagementSetup} provided by the library. \emph{Networking} (SDK) was removed from this diagram for the sake of simplicity. Instantiating \emph{PartDataManagementSetup} is the first step for bootstrapping process of the \emph{Consumer} role functionality. This class provides an entry point to initialize all properties, which are injection points of all parts composing this role. It extends the functionality of the \emph{DataManagementSetup} based on the following associated classes: \emph{PartBindingFactory} and \emph{CommunicationContext}.

The \emph{PartBindingFactory} implements the \emph{IBindingFactory} to gather the data recovered from the \emph{Message} instances pulled from a network. The received data is driven to \emph{CommunicationContext} for further encoding and finally pushing it to the cloud services using the configured out-of-band protocol.

The cloud interconnection is realized using the \emph{CommunicationContext}. It implements a message encoder and establishes the out-of-band communication stack.

\begin{wrapfigure}{t}{0.5\textwidth}
      \includegraphics[width=0.49\textwidth]{ImplementationArchitecture.eps}
      \caption{Implementation Architecture}\label{figure4.ImplementationArchitecture}
\end{wrapfigure}

@@

The encoded JSON messages must be transferred to cloud over the network using the selected protocol stack. The Azure supports HTTP, AMQP, and MQTT protocol stacks, which are all standard ones. Consequently, it is possible to apply any available implementation compliant with an appropriate specification to achieve connectivity. In this case, all parameters required to establish semantic and security contexts are up to the gateway responsibility. Alternatively, the API offered by the dedicated frameworks (libraries) may be used. Using a framework the configuration process may be reduced significantly, and the communication protocol selection has only an indirect impact on the interoperability features. In the proposed implementation, the Azure interconnection has been obtained using the mentioned above frameworks.

@@

We derived the final model presented in Fig. \ref{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig. \ref{figure1.StrategyDomainModel}). In the proposed approach the \emph{Embedded Gateway} is derived from the \emph{Consumer} role implemented as a composable part aggregated by the \emph{Reactive Application}.
